Plots for Latent Hawkes Paper

### 2021-12-28 output_scripts/Paper_Plots.Rmd
tidy up repo some more. delete files which aren't needed, rename some to be more standard

data_path <- "../output/revisions/lapl_check/"

@@

```{r fig-8a-mae-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

@@

```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE, fig.width=8, fig.height=4}
### updated to revision
load("../output/revisions/lapl_check/plot_N_predict_revision.RData")

>>>>

# data_path <- "../output/revisions/lapl_check/"

@@

```{r fig-8a-mae-norm-cohort5, fig.width=8,fig.height=4,eval=TRUE}
load("../output/revisions/aug_run/plot_N_predict_revision.RData")
current_cohort <- 5 # cohort 1 looks worse than rest

@@

```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE, fig.width=8, fig.height=4}
### updated to revision
load("../output/revisions/aug_run/plot_N_predict_revision.RData")
